Measuring efficiency of the greedy-like heuristics for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization

### 2020-10-05 doc/paper.tex
Section 1.2: a comment
update

	\subsection{Discretization}  
	The discretization $D(P)$ of the polygon $P$ is builded as follows. Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of P, where \\
$ \bigtriangleup_{x}=min\{ |u_{x}-v_{x}|,\ u_{x}\neq v_{x}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$ and\\
$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$. \fxnote{tekst ne bi trebao biti italic, koristiti mbox naredbu ili mathrm}

@@

	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.\fxnote{Ova recenica je nejasna, moze li malo bolji prevod?} The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.

	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, obajsniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}

>>>>

	\subsection{Discretization}  
	The discretization $D(P)$ of the polygon $P$ is builded as follows. Consider the regular grid with resolution $\bigtriangleup_{x}\times\bigtriangleup_{y}$ starting at the lower left corner of the bounding box of P, where \\
$ \bigtriangleup_{x}=min\{ |u_{x}-v_{x}|,\ u_{x}\neq v_{x}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$ and\\
$ \bigtriangleup_{y}=min\{ |u_{y}-v_{y}|,\ u_{y}\neq v_{y}\ |\  u,v\ adjacent\ vertices\ of\ the\ polygon\ P \}$. \fxnote{tekst ne bi trebao biti italic, koristiti mbox naredbu ili mathrm, min je naredba u latexu  "min", mjesto $"|"$ korisititi naredbu "mid" }

@@

	The intersection points of this grid that are interior to $P$ and all vertices from $P$ are added to the set $D(P)$.\fxnote{Ova recenica je nejasna, moze li malo bolji prevod? Referisi u odnosu na Pseudokod} The pseudocode for building the discretizations $D(P)$ is given in Algorithm~\ref{alg:discret}.

	\fxnote{TODO: zasto uzimamo ovakav tip diskretizacije, objasniti zasto id pokrivenosti diskretizacije ne slijedu pokrivenost poligona -- dvije slike}
